Probabilistic Model of Bilateral Lymphatic Spread in Head and Neck Cancer

### 2024-10-23 manuscript.qmd
finish visualization of bilateral algebra

![Visual representation of @eq-bilateral-marginal-algebra for the case of midline extention. The left and right matrix represent the evolution of the possible hidden states for the ipsi- and contralateral neck respectively. In particular, the right matrix describes the evolution of the contralateral hidden states *and* midline extension. In the center, the time-prior for EARLYorLATE T-category is plotted as a diagonal matrix. The result of this matrix computation is the joint distribution $P \left( \mathbf{X}^\text{i}, \mathbf{X}^\text{c}, \epsilon=\texttt{True} \right)$](figures/fig_model_state_dist.svg){#fig-model-algebra-equation}

>>>>

![Visual representation of @eq-bilateral-marginal-algebra for the case of midline extention. The left and right matrices represent the evolution of the possible hidden states for the ipsi- and contralateral neck respectively. In particular, the right matrices describe the evolution of the contralateral hidden states once for the case of no midline extension (top) and once for the case where the tumor does extend over the mid-sagittal line (bottom). In the center, the time-prior for late T-category is plotted as a diagonal matrix. The result of this matrix computation is the joint distribution $P \left( \mathbf{X}^\text{i}, \mathbf{X}^\text{c}, \epsilon \right)$](figures/fig_model_algebra_equation.svg){#fig-model-algebra-equation}
